### 2017-02-26 Lab_1/solutions/L1-12-2.tex
Finished Lab1 answers. Added .gitignore for latex files

Minimum: 0.853ms
Maximum: 1.536ms
Average: 1.194

Faster: not via AP but direct

>>>>

Minimum RTT: 0.853ms\\
Maximum RTT: 1.536ms\\
Average RTT: 1.194ms\\\\

Looking at the average RTT, this is 12\% faster than in managed mode. The frame no longer travels via the AP. The additional physical distance to be covered by the signal, plus the processing time at the AP explains why the RTT in exercise 4 is higher. \\ \\
Note that the physical distance between STA1 and AP, and between STA1 and STA2 are roughly the same. This means the direct transmission in ad-hoc mode for this specific ping does not have to travel significantly farther than when the AP was involved.
